---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# TGMRF

<!-- badges: start -->
<!-- [![CRAN status](https://www.r-pkg.org/badges/version/FLAMES)](https://cran.r-project.org/package=FLAMES) -->
<!-- [![Travis build status](https://travis-ci.org/DouglasMesquita/FLAMES.svg?branch=master)](https://travis-ci.org/DouglasMesquita/FLAMES) -->
<!-- [![Codecov test coverage](https://codecov.io/gh/DouglasMesquita/FLAMES/branch/master/graph/badge.svg)](https://codecov.io/gh/DouglasMesquita/FLAMES?branch=master) -->
<!-- badges: end -->

## Overview

TGMRF: Transformed Gaussian Markov Random Fields is a package that allow the use of several approaches to fit Poisson intensities.

## Installation

```{r eval = FALSE}
# Install from CRAN (when available)
install.packages("TGMRF")
# Or the development version from GitHub
# install.packages("devtools")
devtools::install_github("DouglasMesquita/TGMRF")
```

## Usage

`library(TGMRF)` will load **tgmrf**, a function to fit Poisson regression models. The user can choose for several approaches to model the poisson intensities: **gamma-precicison**, **gamma-shape**, **gamma-scale** and **log-normal**.

See `?tgmrf` for examples.
